---
title: "ETW's Data Analysis Plan"
output: html_notebook
---


##Reading In Actigraphy Data First
```{r}
rm(list = ls())
setwd("C:/Users/Ellita/Documents/BioStatIndp/AllData")
#reading in csv of actigraphy
juju <- read.csv(file = "001.CSV", header = FALSE, skip = 146)
```

##Naming Columns and Removing An Unwanted Column at the End of The Actigraphy Dataset
```{r}
#naming the columns of the actigraphy data
colnames(juju) <- c("Line", "Day", "Date", "Time", "Offwrist",
                       "Activity","Marker", "whiteLight","redLight","greenLight",
                       "blueLight", "SleepWake", "IntervalStatus")
#removing the unwanted, empty 14th column in the acitgraphy data
juju <- juju[, 1:13]
```

##Removing Days When Actigraphy Was Not on 001's Wrist, But still Collecting Information per the 7-day protocol
```{r}

#removing the empty days of actigraphy when the patient did not have the watch on
juju <- juju[-c(8167:20160), ]
```

##Converting Standard 12 Hour in 24 HRS scale for Actigraphy
```{r}
#making 24hr time schedule of the actigraphy data
juju$datetime <-as.POSIXct(paste(juju$Date,juju$Time), format = "%m/%e/%Y%I:%M:%S %p")
```


#Removing Unwanted Columns From Actigraphy Data:
* "Line"
* "White"", "Blue"", "Red"", "Green" light
* "Date"
* "Time"
* "Marker"
* "OffWrist"
* "Day"
```{r}
#removing the line number of the data
juju$"Line" <- NULL
#removing all of the light information
juju$"whiteLight" <- NULL
juju$"greenLight" <- NULL
juju$"blueLight" <- NULL
juju$"redLight" <- NULL
juju$"Date" <- NULL
juju$"Time" <- NULL
juju$"Marker" <- NULL
juju$"Offwrist" <- NULL
juju$"Day" <- NULL
```

##Hard-Cut of Actigraphy Data to Match Protoport Data (looked at protoport data earlier)
```{r}
#hard cut of Actigraphy data to match the data points in the protoport
juju <- subset(juju, juju$datetime >= as.POSIXct('2016-06-27 14:13:30') & juju$datetime <= as.POSIXct('2016-06-28 12:30:30'))

```

#Reading in Protoport Data, Naming Columns
```{r}
# reading in protoport data
bean <- read.csv(file = "GN_001_Protoport.TXT", header = FALSE)

#name columns of protoport
colnames(bean) <- c("datetime", "LUX", "MOVE", "SOUND")

```

##Converting Standard 12 Hour in 24 HRS scale for Protoport
```{r}
#converting time in protoport
bean$datetime <- as.POSIXct(bean$datetime, format= "%m/%e/%Y %H:%M:%S")

```

## Removing Duplicates in Protoport, Making NA's in "LUX" variable "0"
```{r}
#removing duplicates
bean <-subset(bean, !duplicated(bean$datetime))
bean$LUX[(is.na(bean$LUX))]<- 0
head(bean, n = 30)
```

Aggregating Proport Data from 1 second to 30 second epochs
```{r}
#aggregating protoport data to 30 sec intervals
bean30 <- aggregate(x= bean, by = list(cut(bean$datetime, breaks = "30 sec")), FUN = mean)
```



